\sysfull

### 2019-10-02 paper/TOSN/evaluation.tex
revision of Table 4
remove space for footnote 2

\begin{table}[t]%

\caption{Comparison of \sys performance running the \textit{sort} application on two different capacitor sizes. We see that \sys optimizes its coalesced task size based on the energy buffer size.
\textbf{Coalesced task} refers to the first coalesced task after a reboot, \textbf{Exp. time} shows the experiment duration, the \textbf{Runs} column lists the number of complete runs of the application during the experiments. \textbf{Run time} is the device collective uptime needed to finish a single iteration of the \textit{sort} application.}
\label{tab:dif_cap}

\begin{minipage}{\columnwidth}
\begin{center}
\begin{tabular}{llllll}
  \toprule
    \textbf{Cap. size} ($\mu\text{f}$)& \textbf{Exp. time} ($s$)& \textbf{on/off cycle} & \textbf{Coalesced task} ($ms$)   & \textbf{Runs} & \textbf{Run time} ($ms$) \\
        \hline
    47                 &1205             & 12.93\%    & 33                        & 85       & 183      \\
    470                &1205             & 12.79\%    & 88                        & 87       & 177 \\
  \bottomrule
\end{tabular}
\end{center}
\end{minipage}  
\end{table}%

@@

Due to its static progressing behavior, Alpaca was unable to complete the \textit{fft} benchmark on distances larger than 15\,cm
% \footnote{At distances greater than 15\,cm, energy incoming during
% execution is negligible and the stored energy is insufficient to complete some of the static tasks.}. 
\footnote{At distances less than 15\,cm the total amount of energy available for task execution includes significant amount of harvested-while-executing energy in addition to the stored energy.}.

>>>>

\begin{table}
\begin{center}
\begin{tabular}{c c c c c c}
  \toprule
    \textbf{Cap. size} ($\mu\text{F}$)& \textbf{Exp. time} ($s$)& \textbf{on/off cycle} & \textbf{Coalesced task} ($ms$)   & \textbf{Runs} & \textbf{Run time} ($ms$) \\
        \hline
    47                 &1205             & 12.93\%    & 33                        & 85       & 183      \\
    470                &1205             & 12.79\%    & 88                        & 87       & 177 \\
  \bottomrule
\end{tabular}
\end{center}
\caption{Comparison of \sys performance running the \textit{sort} application on two different capacitor sizes. We see that \sys optimizes its coalesced task size based on the energy buffer size.
	\textbf{Coalesced task} refers to the first coalesced task after a reboot, \textbf{Exp. time} shows the experiment duration, the \textbf{Runs} column lists the number of complete runs of the application during the experiments. \textbf{Run time} is the device collective uptime needed to finish a single iteration of the \textit{sort} application.}
\label{tab:dif_cap}
\end{table}%

@@

Due to its static progressing behavior, Alpaca was unable to complete the \textit{fft} benchmark on distances larger than 15\,cm\footnote{At distances less than 15\,cm the total amount of energy available for task execution includes significant amount of harvested-while-executing energy in addition to the stored energy.}.
